---
title: "Activity 4 - Day 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r libraries, message=FALSE}
library(tidyverse)
library(tidymodels)
library(GGally)
```


## Load Data
```{r loaddata, message=FALSE}
evals <- readr::read_tsv("https://www.openintro.org/data/tab-delimited/evals.txt")
```
### The Data
```{r plot score}
evals %>% 
  ggplot(aes(x=score)) + 
  geom_histogram(bins = 24) + 
  theme_bw()
```

The distribution of score appears to be left skewed.

```{r plot 2 other variables}
evals %>% 
  ggplot(aes(x=age,y=bty_avg)) + 
  geom_point() + 
  theme_bw()
```

There does not appear to be a strong relation between `bty_avg` and `age`. There may be a weak negative relationship.

## Pairwise Relationships
```{r pairwise}
evals %>% 
  select(starts_with("bty_")) %>% 
  ggpairs() +
  theme_bw()
```
The relationship between all of these variables appear to be positive. `bty_m1low` seems to have the weakest correlations with the 3 variables starting with `bty_f`. It does not make sense to include all of these beauty variables in our model.

### MLR: One Quantitative predictor and One Qualitative Predictor
```{r mlr-gender}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
tidy(m_bty_gen)
```

The predictor `bty_avg` is a significant in explaining the variance in score. The inclusion of the variable `gender` increase the parameter estimate for `bty_avg`.

The formula for male professors is 3.747 + .074`bty_avg` + 0.172

Therefore, if two professors have the same beauty rating, the male professor will have a score that is 0.172 higher than the female.

```{r mlr-rank}
m_bty_rank <- lm(score ~ bty_avg + rank, data = evals)
tidy(m_bty_rank)
```

## Day 2 - Interaction Terms and Other Considerations

### bty_avg x gender interaction
```{r interaction}
m_int <- lm(score ~ bty_avg * gender, data = evals)
tidy(m_int)
```

`bty_avg:gendermale` means that this variable is the interaction between `bty_avg` and if the professor was male.

The interaction equation would be 
`score` = 3.95 + (0.031 + 0.079 * `gendermale`) * `bty_avg` - 0.184 `gendermale`
or for male professors
`score` = 3.76 + 1.1 * `bty_avg` 
and for female professors
`score` = 3.95 + 0.031 * `bty_avg` 

For two professors of different genders have the same beauty scores, the male counterpart will have the higher score.

```{r fit}
summary(m_int)
summary(m_bty_gen)
```
The r-squared value for `m_int` is 0.0712 and `m_bty_gen` is 0.0591, so `m_int` is a better model for explaining the variation in `score`.

### bty_avg x ranking interaction
```{r interaction2}
m_int_rank <- lm(score ~ bty_avg * rank, data = evals)
tidy(m_int_rank)
```

The interaction equation would be
`score` = 4.098 + (0.041 - (0.026 * `ranktenure_track`) + (0.065 * `ranktenured`)) * `bty_avg` - 0.018 * `ranktenure_track` - 0.409 * `ranktenured`
or for tenure track professors
`score` =
for tenured professors
`score` = 
and for teaching professors
`score` =